Simulation Explorer

### 2018-10-25 inst/rmd/vis_sim.Rmd
Update vis_sim function and add example to help file

Row
--------------------------------------------------------------------------------

@@

Row
--------------------------------------------------------------------------------

@@

@@

>>>>

Row {.tabset}
--------------------------------------------------------------------------------

@@

### Recruitment

```{r}
plot_trend(sim, sum_ages = min(sim$ages))
```

@@

### Abundance at length

```{r}
plot_surface(sim, mat = "N_at_length", xlab = "Length", zlab = "N")
```

@@

Survey { `r if(!"setdet" %in% names(sim)) ".hidden"`}
================================================================================

```{r}
sliderInput("samp_year", "Year", 
            min = min(sim$years), max = max(sim$years), 
            value = 1, step = 1)
sliderInput("samp_sim", "Simulation", 
            min = min(sim$setdet$sim), max = max(sim$setdet$sim), 
            value = 1, step = 1)
```

### Survey sampling

```{r, eval = "setdet" %in% names(sim)}
renderPlotly({
  plot_survey(sim, which_year = input$samp_year, which_sim = input$samp_sim)
})
```

Estimates { `r if(!"age_strat_error" %in% names(sim)) ".hidden"`}
================================================================================

```{r}
selectInput("set_den", "Set density", 
            choices = sort(unique(sim$surveys$set_den)))
selectInput("lengths_cap", "Lengths cap", 
            choices = sort(unique(sim$surveys$lengths_cap)))
selectInput("ages_cap", "Ages cap", 
            choices = sort(unique(sim$surveys$ages_cap)))
selectInput("fan_length", "Length", 
            choices = sim$lengths)
selectInput("fan_age", "Age", 
            choices = sim$ages)
```

Column {.tabset}
--------------------------------------------------------------------------------

```{r, eval = "age_strat_error" %in% names(sim)}
renderPlotly({
  s <- sim$surveys
  i <- s$survey[s$set_den == input$set_den & 
                        s$lengths_cap == max(s$lengths_cap) &
                        s$ages_cap == max(s$ages_cap)]
  plot_total_strat_fan(sim, surveys = i)
})
```

### Abundance at length

```{r, eval = "age_strat_error" %in% names(sim)}
renderPlotly({
  s <- sim$surveys
  i <- s$survey[s$set_den == input$set_den & 
                        s$lengths_cap == input$lengths_cap &
                        s$ages_cap == max(s$ages_cap)]
  plot_length_strat_fan(sim, surveys = i, years = sim$years,
                        lengths = input$fan_length, select_by = "length")
})
```

```{r, eval = "age_strat_error" %in% names(sim)}
renderPlotly({
  s <- sim$surveys
  i <- s$survey[s$set_den == input$set_den & 
                        s$lengths_cap == input$lengths_cap &
                        s$ages_cap == input$ages_cap]
  plot_age_strat_fan(sim, surveys = i, years = sim$years,
                        ages = input$fan_age, select_by = "age")
})
```

Error { `r if(!"surveys" %in% names(sim)) ".hidden"`}
================================================================================

Column  {.tabset}
--------------------------------------------------------------------------------

### Error surface by rule

```{r, eval = "surveys" %in% names(sim)}
plot_error_surface(sim, plot_by = "rule")
```

### Error surface by sample size

```{r, eval = "surveys" %in% names(sim)}
plot_error_surface(sim, plot_by = "samples")
```
